### 2019-12-06 paper6/article.tex
Modified reference style.

Advances in microfluidics and nanotechnology have boosted a rapid development of surface engineering in the last two decades. Among the different effects of micro-/nano-patterned surfaces, often inspired by observations in nature, one remarkable finding is that the introduction of micro-/nano-scale roughness on an otherwise smooth hydrophobic surface can sometimes significantly reduce the resistance to an external liquid flow. This slippery effect, due to entrapment of gas or vapor pockets under the surface asperities (superhydrophobic Cassie state), was first observed in the experiment of a water flow through a water-repellent pipe \cite{Watanabe}. Subsequently, a number of studies have demonstrated various levels of drag reduction \cite{Ou,Choi_Kim,Schaffel,Lee}, but also in some cases drag enhancement \cite{Steinberger,Karatay}. Despite the discrepancies in the literature, a common technological challenge for the application of superhydrophobic materials is their fragility \cite{Bocquet}. Under high pressures or external forces, such as turbulent fluctuation or phase change, the surface texture can be partially or fully impregnated by the outer fluid (Cassie-to-Wenzel transition), causing the system to lose the features it was designed for \cite{Gentili,Giacomello, Seo_etal_18}.

Liquid-infused surfaces (LIS) are an alternative when aiming for drag reduction. They are more robust against pressure-induced failure, while displaying the same useful properties as conventional gas-cushioned superhydrophobic surfaces \cite{Wexler}. Two recent experiments have demonstrated, using microfabricated oil-impregnated pillars and grooves separately, up to 16\% drag reduction in laminar flows \cite{Solomon} and up to 14\% drag reduction in turbulent flows \cite{Rosenberg}. In the case of the turbulent flow, the authors also tested superhydrophobic surfaces and measured approximately 10\% drag reduction \cite{Rosenberg}.
\Ge{The values cited above, obtained at small lubricant-to-external-fluid viscosity ratios, can eventually decrease to nearly zero as the lubricant becomes more viscous. However, hybrid designs have been devised to maintain the performance, see \eg a recent proof-of-concept study \cite{Hemeda}.}

Analytically, the slippage over a superhydrophobic or liquid-infused surface can be characterized by an effective slip length. Analogous to the definition of the Navier slip, the effective slip length is an \textit{averaged} quantity equal to the distance below the surface at which the velocity would extrapolate to zero (to be distinguished from the \textit{intrinsic} slip of molecular nature \cite{Gentili}). Extensive studies have been devoted to obtaining theoretical expressions of the effective slip for two-dimensional longitudinal or transverse grooves \cite{Lauga_Stone, Sbragalia_Prosperetti, Davis_Lauga, Ng_Wang, Schonecker, Nizkaya, Crowdy_long, Crowdy_tran}.
\Ge{Among these, \cite{Lauga_Stone, Sbragalia_Prosperetti, Davis_Lauga, Ng_Wang, Crowdy_tran} assume perfect slip along the liquid-gas interface, \cite{Ng_Wang, Schonecker, Nizkaya} assume flat menisci, while the meniscus deformation, if considered, is either small \cite{Crowdy_long, Crowdy_tran} or in the dilute limit (\ie the surface is mostly solid) \cite{Lauga_Stone}. Furthermore, for purpose of calculation, the shape of the interface is always assumed symmetric (\ie flat or circular) even under shear. This practically limits the application of the analytical results to the zero capillary limit, being the upper/lower bound of the drag reduction depending on the specific conditions.}

Understanding the dependence of the slip length on the imposed shear and the lubricant viscosity in more realistic conditions may require a numerical approach. %, able to solve the details of the flow reducing the underlying assumptions.
\Ge{There are, as yet, surprisingly few fully resolved hydrodynamic simulations able to solve the details of the flow reducing the underlying assumptions. Most prior numerical studies still consider flat/circular menisci with zero subphase viscosity \cite{Davies_etal, Martell_Perot_Rothstein, Cheng_Teo_Khoo, Wang_Teo_Khoo,Teo_Khoo_14, Seo_etal_18}; however, they extend analytical solutions to more complex surface patterns or the finite-Reynolds-number regime. Flexible bubble shapes were first considered in \cite{finland} for a uniform gas mattress, and later for a non-uniform distribution \cite{finland2}. Using a two-phase Lattice Boltzmann method, \cite{finland, finland2} show that increasing the capillary number reduces the effective slip, even below zero (\ie more friction than a solid plate). Specifically, their nanobubbles protrude strongly into the flow and remain trapped in the pores. Indeed, for very large protrusion angles, negative slip is both observed experimentally \cite{Steinberger} and verified analytically \cite{Davis_Lauga}. On the other hand, when the protrusion angle is smaller and the bubbles are allowed to slide on the substrate, the phase field simulation of \cite{Gao_Peng} shows the opposite behavior: the effective slip is nearly shear-independent for relatively low capillary numbers, while it can increase dramatically if the capillary number is beyond some threshold. This threshold is not a single, universal value but depends on the spacing of the grooves and the initial filling of the gas; however,  the enhancement of the slip is clearly due to depinning of the liquid-gas-solid contact line. We note that the depinning process considered in \cite{Gao_Peng} might be an idealization, since realistic solid surfaces may not be smooth/chemically-homogeneous near the edge. Furthermore, both studies consider gas bubbles submerged in water under unrealistically large shear rates ($10^6 \sim 10^7 s^{-1}$)\footnote{In \cite{finland}, the shear rates were reported as $10^{-6} \sim 10^{-7} s^{-1}$. This must be a typo.}. Whether this is stable or can be physically realized without generating significant heat remains an open question.}

@@

We consider the transverse flow over an array of regularly spaced square cavities illustrated in Fig.\ \ref{fig: schematic}. The outer fluid of viscosity $\mu_1$ is driven by a constant shear $\dot{\gamma}$ in the $x$ direction, imposed at distance $H$ above the floor. The cavities of length $L/2$ and depth $H/2$ are partially filled with a lubricant fluid of viscosity $\mu_2$. When the number of the microcavities is large, the system is equivalent to a single cavity with periodic boundary conditions in the front and back. The solution at the (quasi-)steady state is determined by the incompressible Stokes equations, written in the non-dimensional form
\begin{equation} \label{Stokes}
  \begin{aligned}
    \nabla \cdot {\bm u} = 0, \quad
    -\nabla p + \nabla \cdot \big[ \mu_i ( \nabla {\bm u} + \nabla {\bm u}^T ) \big] = 0,
  \end{aligned}
\end{equation}
where ${\bm u}=(u,v)$ is the velocity, $p=p(x,y)$ the pressure, and $\mu_i=\tilde{\mu}_i/\tilde{\mu}_1$ ($i=$ 1 or 2) the dimensionless viscosity, using $\tilde{H}$ and $\dot{\tilde{\gamma}} \tilde{H}$ as the reference length and velocity respectively\Ge{\footnote{Dimensional values are denoted with a tilde throughout the manuscript.}}. For viscous flows, the velocity and its tangential derivatives are continuous along the fluid interface \cite{Batchelor}. The normal stress is discontinuous due to the surface tension $\tilde{\sigma}$ and the viscosity difference, giving the pressure jump (denoted as $[A]_\Gamma=A_2-A_1$)
\begin{equation} \label{p jump}
  [p]_\Gamma = \frac{\kappa}{\textrm{Ca}} + 2[\mu]_\Gamma {\bm n}^T \cdot \nabla {\bm u} \cdot {\bm n} 
  \quad \textrm{on} \quad \Gamma,
\end{equation}
where ${\bm n}$ is the outward-pointing normal at the interface $\Gamma$, $\kappa$ its curvature, and Ca $=\tilde{\mu}_1 \dot{\tilde{\gamma}} \tilde{H}/\tilde{\sigma}$ the capillary number.

@@

\Ge{In the following, we will consider various combinations of the governing parameters \textit{(i--v)} and evaluate $\lambda_e$ for each configuration. As the result will clearly depend on the motion of the impregnated lubricant, the multiscale modelling approach that we adopt is described next. The objective here is to provide an overall description of our methodology, rather than deriving the full mathematical/numerical details. For the latter, including validations, we refer to our previous work \cite{Martin, Hanna}.}

@@

\Ge{We model the contact line dynamics in two steps.} First, we solve the Cahn-Hilliard equations within a Stokes system
\begin{equation} \label{C-H}
  \frac{\partial c}{\partial t} + \tilde{{\bm u}}\cdot \nabla c -\tilde{m}\nabla ^2 \tilde{\psi}=0,
  \quad \tilde{\psi} - \frac{3\tilde{\sigma} \tilde{\epsilon}}{4} 
  \bigg(\frac{2}{\tilde{\epsilon}^2}(c^3-c) -\nabla ^2 c \bigg) =0,
\end{equation}
\begin{equation} \label{C-H Stokes}
    \nabla \cdot \tilde{{\bm u}} = 0, \quad
    -\nabla \tilde{p} + \nabla \cdot 
    \big[ \tilde{\mu} ( \nabla \tilde{{\bm u}} + \nabla \tilde{{\bm u}}^T ) \big] +\tilde{\psi}\nabla c = 0.
\end{equation}
In the above, $c$ is a non-dimensional phase parameter smoothly varying from $+1$ in one fluid to $-1$ in the other within a thickness of $\tilde{\epsilon}$, $\tilde{\psi}$ is the fluid chemical potential, $\tilde{m}$ is the mobility, and $\tilde{\sigma}$, again, is the surface tension. The chemical potential $\tilde{\psi}$ measures the variation of the system free energy with respect to $c$. Its gradient determines the interfacial diffusion flux $-\tilde{m}\nabla \tilde{\psi}$, which together with the convective flux $\tilde{{\bm u}} c$, models the creation, movement, and dissolution of phase interfaces \cite{Jacqmin2000}. %More detailed descriptions of the mechanism for the contact line motions modelled by the Cahn-Hilliard equations can be found in \cite{Jacqmin2000}.

@@

\Ge{The steady-state solutions of Eqs.\ (\ref{C-H}--\ref{C-H Stokes}) give the contact line velocity, $\chi u_c(\theta)$, function of the apparent contact angle only. It is typically nonlinear, and is valid down to the nanometer scale. To impose this slip velocity in the micrometer cavity flow, as the second step, we modify the velocity boundary condition near the contact line using asymptotic matching \cite{Hanna}. Here, the self-similarity of the local velocity field is invoked and the singularity of the viscous stress is avoided \cite{Huh_Scriven}. The end result is an algebraic operator, ${\bm \Theta}(y)$, applied to $\chi u_c(\theta)$ on the boundary $\partial \Omega_\Gamma$.}

\Ge{%The above two steps together yield the final slip velocity given in Eq.\ \eqref{slip bc}. 
We comment that our multiscale modelling approach is not limited to the phase-field model for the nanoscale; in principle, any model able to describe the contact line dynamics, \eg the molecular dynamics (MD) \cite{Johansson} or the Lattice-Boltzmann (LB) \cite{Sbragaglia_etal}, can be used. We also note that, by solving Eqs.\ (\ref{C-H}--\ref{C-H Stokes}) in a square domain, we implicitly assume the solid surface is nanosmooth.}
%Lastly, it is worth noting that our model implicitly assumes a perfectly smooth solid surface at the continuum level.
Consequently, any deviation from the static contact angle will result in an interface displacement, bringing the phase field back to its local equilibrium. In practice, a real surface may have random roughness or defects smaller than the scale of the printed patterns, causing the interface to be pinned (\ie contact angle hysteresis). Such effects can be included by modifying the geometry of the computational domain, or simply by modifying the relation $u_c=u_c(\theta)$ so that $u_c=0$ for a range of $\theta$'s. %Such effects can be modelled by modifing the $u_c=u_c(\theta)$ relation, so that $u_c=0$ for a range of $\theta$ according to empirical values. To focus on the controlled physical effects, we assume here the cavity has an ideal surface.
\Ge{In Sec.\ \ref{results}, we will take this second approach to account for a small contact angle hysteresis.}

@@

The governing equations, together with the boundary conditions, Eqs.\ (\ref{Stokes}--\ref{slip bc}), are solved numerically using the two-phase flow solver described in \cite{MartinHPC}, with suitable modifications for moving contact lines. The equations are discretized in space using the finite element method and the solver is implemented in the C++ based finite element open source library \texttt{deal.II} \cite{DEAL1, DEAL2}.
\Ge{The interface between the two fluids is evolved using the conservative level set method \cite{CONSLS}, so that only one fixed set of mesh is required. Specifically, we use uniformly distributed quadrilaterals (\ie squares) with grid spacing $\Delta x=1/160$, and time steps restricted by the stability condition $\Delta t_{max} = c_0$Ca$\Delta x$ ($c_0$ is a constant) \cite{MartinHPC}. This leads to $\Delta t =10^{-4} \sim 10^{-3}$ depending on the capillary number Ca. }

@@

We study the effective slip over microcavities partially filled with a second fluid using the parameters summarized in Tab.\ \ref{tab: param}.
%by varying the viscosity ratio $\tilde{\mu}_2/\tilde{\mu}_1$, the capillary number $Ca=\tilde{\mu}_1 \dot{\tilde{\gamma}} \tilde{H}/\tilde{\sigma}$, the static contact angle $\theta_s$, and the \Ge{filling fraction} of the cavity \Ge{$\delta=2d_0/H$}. The contact line velocity is obtained from the local phase field model, using the physical properties of the two fluids as summarized in Tab.\ \ref{tab: param}. 
Here, six pairs of fluids are considered as in the experiment \cite{Solomon}, leading to a wide range of $\tilde{\mu}_2/\tilde{\mu}_1$ from $31.7$ to $3.83\e{-3}$. \Ge{The filling fraction is initialized to $\delta=0.94$ (corresponding to a depth $d_0=0.47H$) to allow for some sloshing of the lubricant.} The velocity ratio $\chi=\tilde{U}_c/ (\dot{\tilde{\gamma}} \tilde{H})$ is set constant for all the fluid pairs and shear rates to reduce the number of parameters and focus on the single physical effects mentioned above. This also implies that the capillary number is varied by changing the outer fluid viscosity. As an example, for $\dot{\tilde{\gamma}}=800$ s$^{-1}$, $\tilde{H}=20$ $\mu$m, and $\tilde{U}_c=2.63$ m/s, 
%(see \cite{dimension} for the detailed estimation), 
the velocity ratio $\chi \approx 164$ (which is indeed much greater than 1), and the corresponding Ca increases from $1.92\e{-3}$ to $1.59$ for the different viscosities considered.\footnote{We estimate the dimensional shear rate at the upper boundary of our computational domian from the experimental Hele-Shaw setup in \cite{Wexler} (2 mL/min through a cross-section of 180 $\mu$m $\times$ 7 mm). Assuming a parabolic velocity profile, the reference velocity at $\tilde{H}=20$ $\mu$m is $\tilde{U}=$ 0.016 m/s, leading to a shear rate of $\dot{\tilde{\gamma}}=800$ s$^{-1}$. The characteristic contact line velocity is calculated as $\tilde{U}_c=\tilde{\sigma}/\tilde{\mu}_2$, taking $\tilde{\sigma}=0.02$ kg/$s^2$ and $\tilde{\mu}_2=0.0076$ $\nicefrac{kg}{ms}$, as in \cite{Martin}} We further modify Ca at a fixed $\chi$ to study the effect of interface deformation. Finally, the effect of the static contact angle is investigated by considering $\theta_s=80\degree$ (leading to a convex meniscus), $\theta_s=105\degree$ (concave meniscus), \Ge{and $\chi u_c(\theta)=0 $ for $\theta_s \in [76\degree, 84\degree ]$ to mimic some contact angle hysteresis.}

@@

\Ge{As we vary $\tilde{\mu}_2/\tilde{\mu}_1$ over four orders-of-magnitude, Fig.\ \ref{fig:tabulated} reveals a non-trivial dependence of the contact line dynamics. On the one end, $\chi u_c$ changes rapidly with $\theta$ for very viscous lubricants, almost diverging for $\theta < 60\degree$ in the case of $\tilde{\mu}_2/\tilde{\mu}_1=31.7$; on the other end, as the lubricant becomes less and less viscous, the $\chi u_c (\theta)$ relations eventually collapse onto one curve. Qualitatively, reduction of $\chi u_c$ for decreasing $\tilde{\mu}_2/\tilde{\mu}_1$ is expected as we normalize the flow using the shear in the outer fluid; in other words, it is easier (hence requires less velocity) to displace a less viscous fluid (\ie deviating $\theta$ from $\theta_s$). In addition, the change of the curvature of the function $\chi u_c ( \theta)$  can be inferred from the reciprocity of the two fluids (\ie $-\chi u_c$ instead of $\chi u_c$ and $ 180-\theta$ instead of $\theta$ for the same $\tilde{\mu}_1/\tilde{\mu}_2$)\footnote{This is merely a qualitative argument, as it does not preserve the static angle unless $\theta_s=90\degree$.}. Quantitatively, the present model has been compared favorably with Cox' law \cite{COX}, especially for small angle deviations \cite{Martin}. Since this is the regime where the fluids normally operate at, we expect our model to accurately capture the small-scale contact line motions.}

@@

%there many different models for dynamic wetting, based on hydrodynamic theories, molecular-kinetic theories, molecular dynamics, \etc \cite{Blake,...,GNBC}. None of these models are complete; however, censensus is still lacking. It shouldn't affect the overall qualitative results.

@@

\Ge{We remark that constant shear stress along substrate surfaces is sometimes assumed in theoretical models to obtain analytical  solutions \cite{Schonecker}. Although it is verified for fully-covered flat cavities (see Fig.\ 4 in \cite{Schonecker}), our results suggest that it is inaccurate for partially filled ones, even along the fluid-fluid interface, see Fig.\ \ref{fig: stress}(b). Since liquid-infused substrates are not always fully-covered in practice \cite{Wexler}, our simulations suggest this assumption be relaxed when developing more comprehensive models.}

@@

\Ge{The above phenomenological mechanism suggests that, taking the lubricant viscosity as a design parameter, the intermediate viscosity ratios (\eg $\tilde{\mu}_2/\tilde{\mu}_1 = 0.01 \sim 1$ depending on the specific condition) are to be avoided in the application of LIS. This is consistent with previous experiments of longitudinal grooves towards the lower viscosity branch \cite{Liu}; 
more viscous lubricants, on the other hand,  seem to ensure higher robustness.}

>>>>

Advances in microfluidics and nanotechnology have boosted a rapid development of surface engineering in the last two decades. Among the different effects of micro-/nano-patterned surfaces, often inspired by observations in nature, one remarkable finding is that the introduction of micro-/nano-scale roughness on an otherwise smooth hydrophobic surface can sometimes significantly reduce the resistance to an external liquid flow. This slippery effect, due to entrapment of gas or vapor pockets under the surface asperities (superhydrophobic Cassie state), was first observed in the experiment of a water flow through a water-repellent pipe \citep{Watanabe}. Subsequently, a number of studies have demonstrated various levels of drag reduction \citep{Ou,Choi_Kim,Schaffel,Lee}, but also in some cases drag enhancement \citep{Steinberger,Karatay}. Despite the discrepancies in the literature, a common technological challenge for the application of superhydrophobic materials is their fragility \citep{Bocquet}. Under high pressures or external forces, such as turbulent fluctuation or phase change, the surface texture can be partially or fully impregnated by the outer fluid (Cassie-to-Wenzel transition), causing the system to lose the features it was designed for \citep{Gentili,Giacomello, Seo_etal_18}.

Liquid-infused surfaces (LIS) are an alternative when aiming for drag reduction. They are more robust against pressure-induced failure, while displaying the same useful properties as conventional gas-cushioned superhydrophobic surfaces \citep{Wexler}. Two recent experiments have demonstrated, using microfabricated oil-impregnated pillars and grooves separately, up to 16\% drag reduction in laminar flows \citep{Solomon} and up to 14\% drag reduction in turbulent flows \citep{Rosenberg}. In the case of the turbulent flow, the authors also tested superhydrophobic surfaces and measured approximately 10\% drag reduction \citep{Rosenberg}.
\Ge{The values cited above, obtained at small lubricant-to-external-fluid viscosity ratios, can eventually decrease to nearly zero as the lubricant becomes more viscous. However, hybrid designs have been devised to maintain the performance, see \eg a recent proof-of-concept study \citep{Hemeda}.}

Analytically, the slippage over a superhydrophobic or liquid-infused surface can be characterized by an effective slip length. Analogous to the definition of the Navier slip, the effective slip length is an \textit{averaged} quantity equal to the distance below the surface at which the velocity would extrapolate to zero (to be distinguished from the \textit{intrinsic} slip of molecular nature \citep{Gentili}). Extensive studies have been devoted to obtaining theoretical expressions of the effective slip for two-dimensional longitudinal or transverse grooves \citep{Lauga_Stone, Sbragalia_Prosperetti, Davis_Lauga, Ng_Wang, Schonecker, Nizkaya, Crowdy_long, Crowdy_tran}.
\Ge{Among these, \cite{Lauga_Stone, Sbragalia_Prosperetti, Davis_Lauga, Ng_Wang, Crowdy_tran} assume perfect slip along the liquid-gas interface, \cite{Ng_Wang, Schonecker, Nizkaya} assume flat menisci, while the meniscus deformation, if considered, is either small \citep{Crowdy_long, Crowdy_tran} or in the dilute limit (\ie the surface is mostly solid) \citep{Lauga_Stone}. Furthermore, for purpose of calculation, the shape of the interface is always assumed symmetric (\ie flat or circular) even under shear. This practically limits the application of the analytical results to the zero capillary limit, being the upper/lower bound of the drag reduction depending on the specific conditions.}

Understanding the dependence of the slip length on the imposed shear and the lubricant viscosity in more realistic conditions may require a numerical approach. %, able to solve the details of the flow reducing the underlying assumptions.
\Ge{There are, as yet, surprisingly few fully resolved hydrodynamic simulations able to solve the details of the flow reducing the underlying assumptions. Most prior numerical studies still consider flat/circular menisci with zero subphase viscosity \citep{Davies_etal, Martell_Perot_Rothstein, Cheng_Teo_Khoo, Wang_Teo_Khoo,Teo_Khoo_14, Seo_etal_18}; however, they extend analytical solutions to more complex surface patterns or the finite-Reynolds-number regime. Flexible bubble shapes were first considered in \cite{finland} for a uniform gas mattress, and later for a non-uniform distribution \citep{finland2}. Using a two-phase Lattice Boltzmann method, \cite{finland, finland2} show that increasing the capillary number reduces the effective slip, even below zero (\ie more friction than a solid plate). Specifically, their nanobubbles protrude strongly into the flow and remain trapped in the pores. Indeed, for very large protrusion angles, negative slip is both observed experimentally \citep{Steinberger} and verified analytically \citep{Davis_Lauga}. On the other hand, when the protrusion angle is smaller and the bubbles are allowed to slide on the substrate, the phase field simulation of \cite{Gao_Peng} shows the opposite behavior: the effective slip is nearly shear-independent for relatively low capillary numbers, while it can increase dramatically if the capillary number is beyond some threshold. This threshold is not a single, universal value but depends on the spacing of the grooves and the initial filling of the gas; however,  the enhancement of the slip is clearly due to depinning of the liquid-gas-solid contact line. We note that the depinning process considered in \cite{Gao_Peng} might be an idealization, since realistic solid surfaces may not be smooth/chemically-homogeneous near the edge. Furthermore, both studies consider gas bubbles submerged in water under unrealistically large shear rates ($10^6 \sim 10^7 s^{-1}$)\footnote{In \cite{finland}, the shear rates were reported as $10^{-6} \sim 10^{-7} s^{-1}$. This must be a typo.}. Whether this is stable or can be physically realized without generating significant heat remains an open question.}

@@

We consider the transverse flow over an array of regularly spaced square cavities illustrated in Fig.\ \ref{fig: schematic}. The outer fluid of viscosity $\mu_1$ is driven by a constant shear $\dot{\gamma}$ in the $x$ direction, imposed at distance $H$ above the floor. The cavities of length $L/2$ and depth $H/2$ are partially filled with a lubricant fluid of viscosity $\mu_2$. When the number of the microcavities is large, the system is equivalent to a single cavity with periodic boundary conditions in the front and back. The solution at the (quasi-)steady state is determined by the incompressible Stokes equations, written in the non-dimensional form
\begin{equation} \label{Stokes}
  \begin{aligned}
    \nabla \cdot {\bm u} = 0, \quad
    -\nabla p + \nabla \cdot \big[ \mu_i ( \nabla {\bm u} + \nabla {\bm u}^T ) \big] = 0,
  \end{aligned}
\end{equation}
where ${\bm u}=(u,v)$ is the velocity, $p=p(x,y)$ the pressure, and $\mu_i=\tilde{\mu}_i/\tilde{\mu}_1$ ($i=$ 1 or 2) the dimensionless viscosity, using $\tilde{H}$ and $\dot{\tilde{\gamma}} \tilde{H}$ as the reference length and velocity respectively\Ge{\footnote{Dimensional values are denoted with a tilde throughout the manuscript.}}. For viscous flows, the velocity and its tangential derivatives are continuous along the fluid interface \citep{Batchelor}. The normal stress is discontinuous due to the surface tension $\tilde{\sigma}$ and the viscosity difference, giving the pressure jump (denoted as $[A]_\Gamma=A_2-A_1$)
\begin{equation} \label{p jump}
  [p]_\Gamma = \frac{\kappa}{\textrm{Ca}} + 2[\mu]_\Gamma {\bm n}^T \cdot \nabla {\bm u} \cdot {\bm n} 
  \quad \textrm{on} \quad \Gamma,
\end{equation}
where ${\bm n}$ is the outward-pointing normal at the interface $\Gamma$, $\kappa$ its curvature, and Ca $=\tilde{\mu}_1 \dot{\tilde{\gamma}} \tilde{H}/\tilde{\sigma}$ the capillary number.

@@

\Ge{In the following, we will consider various combinations of the governing parameters \textit{(i--v)} and evaluate $\lambda_e$ for each configuration. As the result will clearly depend on the motion of the impregnated lubricant, the multiscale modelling approach that we adopt is described next. The objective here is to provide an overall description of our methodology, rather than deriving the full mathematical/numerical details. For the latter, including validations, we refer to our previous work \citep{Martin, Hanna}.}

@@

\Ge{We model the contact line dynamics in two steps.} First, we solve the Cahn-Hilliard equations within a Stokes system
\begin{equation} \label{C-H}
  \frac{\partial c}{\partial t} + \tilde{{\bm u}}\cdot \nabla c -\tilde{m}\nabla ^2 \tilde{\psi}=0,
  \quad \tilde{\psi} - \frac{3\tilde{\sigma} \tilde{\epsilon}}{4} 
  \bigg(\frac{2}{\tilde{\epsilon}^2}(c^3-c) -\nabla ^2 c \bigg) =0,
\end{equation}
\begin{equation} \label{C-H Stokes}
    \nabla \cdot \tilde{{\bm u}} = 0, \quad
    -\nabla \tilde{p} + \nabla \cdot 
    \big[ \tilde{\mu} ( \nabla \tilde{{\bm u}} + \nabla \tilde{{\bm u}}^T ) \big] +\tilde{\psi}\nabla c = 0.
\end{equation}
In the above, $c$ is a non-dimensional phase parameter smoothly varying from $+1$ in one fluid to $-1$ in the other within a thickness of $\tilde{\epsilon}$, $\tilde{\psi}$ is the fluid chemical potential, $\tilde{m}$ is the mobility, and $\tilde{\sigma}$, again, is the surface tension. The chemical potential $\tilde{\psi}$ measures the variation of the system free energy with respect to $c$. Its gradient determines the interfacial diffusion flux $-\tilde{m}\nabla \tilde{\psi}$, which together with the convective flux $\tilde{{\bm u}} c$, models the creation, movement, and dissolution of phase interfaces \citep{Jacqmin2000}. %More detailed descriptions of the mechanism for the contact line motions modelled by the Cahn-Hilliard equations can be found in \citep{Jacqmin2000}.

@@

\Ge{The steady-state solutions of Eqs.\ (\ref{C-H}--\ref{C-H Stokes}) give the contact line velocity, $\chi u_c(\theta)$, function of the apparent contact angle only. It is typically nonlinear, and is valid down to the nanometer scale. To impose this slip velocity in the micrometer cavity flow, as the second step, we modify the velocity boundary condition near the contact line using asymptotic matching \citep{Hanna}. Here, the self-similarity of the local velocity field is invoked and the singularity of the viscous stress is avoided \citep{Huh_Scriven}. The end result is an algebraic operator, ${\bm \Theta}(y)$, applied to $\chi u_c(\theta)$ on the boundary $\partial \Omega_\Gamma$.}

\Ge{%The above two steps together yield the final slip velocity given in Eq.\ \eqref{slip bc}. 
We comment that our multiscale modelling approach is not limited to the phase-field model for the nanoscale; in principle, any model able to describe the contact line dynamics, \eg the molecular dynamics (MD) \citep{Johansson} or the Lattice-Boltzmann (LB) \citep{Sbragaglia_etal}, can be used. We also note that, by solving Eqs.\ (\ref{C-H}--\ref{C-H Stokes}) in a square domain, we implicitly assume the solid surface is nanosmooth.}
%Lastly, it is worth noting that our model implicitly assumes a perfectly smooth solid surface at the continuum level.
Consequently, any deviation from the static contact angle will result in an interface displacement, bringing the phase field back to its local equilibrium. In practice, a real surface may have random roughness or defects smaller than the scale of the printed patterns, causing the interface to be pinned (\ie contact angle hysteresis). Such effects can be included by modifying the geometry of the computational domain, or simply by modifying the relation $u_c=u_c(\theta)$ so that $u_c=0$ for a range of $\theta$'s. %Such effects can be modelled by modifing the $u_c=u_c(\theta)$ relation, so that $u_c=0$ for a range of $\theta$ according to empirical values. To focus on the controlled physical effects, we assume here the cavity has an ideal surface.
\Ge{In Sec.\ \ref{results}, we will take this second approach to account for a small contact angle hysteresis.}

@@

The governing equations, together with the boundary conditions, Eqs.\ (\ref{Stokes}--\ref{slip bc}), are solved numerically using the two-phase flow solver described in \cite{MartinHPC}, with suitable modifications for moving contact lines. The equations are discretized in space using the finite element method and the solver is implemented in the C++ based finite element open source library \texttt{deal.II} \citep{DEAL1, DEAL2}.
\Ge{The interface between the two fluids is evolved using the conservative level set method \citep{CONSLS}, so that only one fixed set of mesh is required. Specifically, we use uniformly distributed quadrilaterals (\ie squares) with grid spacing $\Delta x=1/160$, and time steps restricted by the stability condition $\Delta t_{max} = c_0$Ca$\Delta x$ ($c_0$ is a constant) \citep{MartinHPC}. This leads to $\Delta t =10^{-4} \sim 10^{-3}$ depending on the capillary number Ca. }

@@

We study the effective slip over microcavities partially filled with a second fluid using the parameters summarized in Tab.\ \ref{tab: param}.
%by varying the viscosity ratio $\tilde{\mu}_2/\tilde{\mu}_1$, the capillary number $Ca=\tilde{\mu}_1 \dot{\tilde{\gamma}} \tilde{H}/\tilde{\sigma}$, the static contact angle $\theta_s$, and the \Ge{filling fraction} of the cavity \Ge{$\delta=2d_0/H$}. The contact line velocity is obtained from the local phase field model, using the physical properties of the two fluids as summarized in Tab.\ \ref{tab: param}. 
Here, six pairs of fluids are considered as in the experiment \citep{Solomon}, leading to a wide range of $\tilde{\mu}_2/\tilde{\mu}_1$ from $31.7$ to $3.83\e{-3}$. \Ge{The filling fraction is initialized to $\delta=0.94$ (corresponding to a depth $d_0=0.47H$) to allow for some sloshing of the lubricant.} The velocity ratio $\chi=\tilde{U}_c/ (\dot{\tilde{\gamma}} \tilde{H})$ is set constant for all the fluid pairs and shear rates to reduce the number of parameters and focus on the single physical effects mentioned above. This also implies that the capillary number is varied by changing the outer fluid viscosity. As an example, for $\dot{\tilde{\gamma}}=800$ s$^{-1}$, $\tilde{H}=20$ $\mu$m, and $\tilde{U}_c=2.63$ m/s, 
%(see \cite{dimension} for the detailed estimation), 
the velocity ratio $\chi \approx 164$ (which is indeed much greater than 1), and the corresponding Ca increases from $1.92\e{-3}$ to $1.59$ for the different viscosities considered.\footnote{We estimate the dimensional shear rate at the upper boundary of our computational domian from the experimental Hele-Shaw setup in \cite{Wexler} (2 mL/min through a cross-section of 180 $\mu$m $\times$ 7 mm). Assuming a parabolic velocity profile, the reference velocity at $\tilde{H}=20$ $\mu$m is $\tilde{U}=$ 0.016 m/s, leading to a shear rate of $\dot{\tilde{\gamma}}=800$ s$^{-1}$. The characteristic contact line velocity is calculated as $\tilde{U}_c=\tilde{\sigma}/\tilde{\mu}_2$, taking $\tilde{\sigma}=0.02$ kg/$s^2$ and $\tilde{\mu}_2=0.0076$ $\nicefrac{kg}{ms}$, as in \cite{Martin}} We further modify Ca at a fixed $\chi$ to study the effect of interface deformation. Finally, the effect of the static contact angle is investigated by considering $\theta_s=80\degree$ (leading to a convex meniscus), $\theta_s=105\degree$ (concave meniscus), \Ge{and $\chi u_c(\theta)=0 $ for $\theta_s \in [76\degree, 84\degree ]$ to mimic some contact angle hysteresis.}

@@

\Ge{As we vary $\tilde{\mu}_2/\tilde{\mu}_1$ over four orders-of-magnitude, Fig.\ \ref{fig:tabulated} reveals a non-trivial dependence of the contact line dynamics. On the one end, $\chi u_c$ changes rapidly with $\theta$ for very viscous lubricants, almost diverging for $\theta < 60\degree$ in the case of $\tilde{\mu}_2/\tilde{\mu}_1=31.7$; on the other end, as the lubricant becomes less and less viscous, the $\chi u_c (\theta)$ relations eventually collapse onto one curve. Qualitatively, reduction of $\chi u_c$ for decreasing $\tilde{\mu}_2/\tilde{\mu}_1$ is expected as we normalize the flow using the shear in the outer fluid; in other words, it is easier (hence requires less velocity) to displace a less viscous fluid (\ie deviating $\theta$ from $\theta_s$). In addition, the change of the curvature of the function $\chi u_c ( \theta)$  can be inferred from the reciprocity of the two fluids (\ie $-\chi u_c$ instead of $\chi u_c$ and $ 180-\theta$ instead of $\theta$ for the same $\tilde{\mu}_1/\tilde{\mu}_2$)\footnote{This is merely a qualitative argument, as it does not preserve the static angle unless $\theta_s=90\degree$.}. Quantitatively, the present model has been compared favorably with Cox' law \citep{COX}, especially for small angle deviations \citep{Martin}. Since this is the regime where the fluids normally operate at, we expect our model to accurately capture the small-scale contact line motions.}

@@

%there many different models for dynamic wetting, based on hydrodynamic theories, molecular-kinetic theories, molecular dynamics, \etc \citep{Blake,...,GNBC}. None of these models are complete; however, censensus is still lacking. It shouldn't affect the overall qualitative results.

@@

\Ge{We remark that constant shear stress along substrate surfaces is sometimes assumed in theoretical models to obtain analytical  solutions \citep{Schonecker}. Although it is verified for fully-covered flat cavities (see Fig.\ 4 in \cite{Schonecker}), our results suggest that it is inaccurate for partially filled ones, even along the fluid-fluid interface, see Fig.\ \ref{fig: stress}(b). Since liquid-infused substrates are not always fully-covered in practice \citep{Wexler}, our simulations suggest this assumption be relaxed when developing more comprehensive models.}

@@

\Ge{The above phenomenological mechanism suggests that, taking the lubricant viscosity as a design parameter, the intermediate viscosity ratios (\eg $\tilde{\mu}_2/\tilde{\mu}_1 = 0.01 \sim 1$ depending on the specific condition) are to be avoided in the application of LIS. This is consistent with previous experiments of longitudinal grooves towards the lower viscosity branch \citep{Liu}; 
more viscous lubricants, on the other hand,  seem to ensure higher robustness.}
